---
title: "Population of Spain's Regional Capitals"
author: "Fabio Alexandre Alberini Lopes Lima"
date: "2 de diciembre de 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About the Data

This project creates a map with the location and population of the capital for each of the 50 regions (Provincias) in Spain.

The geographical coordindinates (latitude and longitude) were taken from this web page: <https://www.businessintelligence.info/varios/longitud-latitud-pueblos-espana.html>

The previous page also provided population information, but since it was outdated, I used information from National Institute of Statistics (INE) to get the updated data (2016) <http://ine.es/jaxiT3/Datos.htm?t=2911>

```{r}
population <- read.csv("2911sc.csv", sep = ";", skip = 7, stringsAsFactors = F, header = F, nrows = 50, encoding = "latin1")
capitals <- sub("/", "-", substr(population$V1, start = 7, stop = 100))
capitals <- sub("Palma de Mallorca", "Palma", capitals)
population <- population[order(capitals),]

coord <- read.csv("listado-longitud-latitud-municipios-espana.csv", sep = ";", skip = 2, stringsAsFactors = F, header = T, dec = ",")

coord$Población <- sub("/", "-", coord$Población)
coord$Población <- sub(" (A)", ", A", coord$Población, fixed = T)
coord$Población <- sub(" (Las)", ", Las", coord$Población, fixed = T)

latlong <- subset(coord, coord$Población %in% capitals, select = c(Población, Latitud, Longitud, Habitantes))
latlong <- latlong[order(latlong$Población),]

names(latlong) <- c("City", "latitude", "longitude", "Population")
latlong$Population2016 <- population$V2
```


## Spain: Regional Capitals

```{r,message=FALSE}
library(leaflet)

spainCapitals <- leaflet(latlong) %>%
      addTiles(urlTemplate = "http://{s}.tile.openstreetmap.org/{z}/{x}/{y}.png") %>%
      addCircleMarkers(label = paste(latlong$City, " (", as.character(latlong$Population2016),")"),
                       radius = sqrt(latlong$Population2016)/100,
                       weight = 1,
                       fillColor = "green")
spainCapitals
```

